### 2022-05-27 main/chapter_2ljets.tex
label and ref rjr summaries; minor cleanup

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$ RJR~\cite{atlas2022searches}}
\end{subfigure}
\caption{%
Summary plots for RJR analyses:
(a) and (b)~two- and three- lepton selections respectively reproduced
from~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$ RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\textit{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26\,\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12\,\eV[G]$ and
\item $\pt^{e_2} > 17\,\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10\,\eV[G]$,
\item $\pt^{\mu_2} > 14\,\eV[G]$,
\item $\pt^{\mu_1} > 18\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$, and
\item $\pt^{\mu_1} > 22\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17\,\eV[G]~\&~\pt^{\mu_1} > 14\,\eV[G]$,
\item $\pt^{e_1} > 7\,\eV[G]~\&~\pt^{\mu_1} > 24\,\eV[G]$, and
\item $\pt^{e_1} > 26\,\eV[G]~\&~\pt^{\mu_1} > 8\,\eV[G]$.
\end{itemize}
\end{itemize}
Please do not read these all in detail.
The point of listing them is that trigger activations are not trivial,
and motivate lepton selections which exceed these trigger thresholds
to avoid trigger activation effects.

@@

\subsection{Jets}

Like leptons, hadronic jets are identified with `baseline' and `signal'
requirements with increasingly tight requirements on quality metrics and
kinematics.

@@

\subsubsection{$b$-tagging}
\label{sec:btagging}

Tagging adds labels to objects.
Unlike how electrons and muons are very cleanly separated however, jet tagging
is a more noisy affair.
Taggers are available for various jet properties, such charm flavor ($c$-jet),
bottom flavor ($b$-jet).
Of these, $\twoljets$ uses only $b$-tagging.

@@

\subsection{Stranverse mass $\mttwo$}
\label{sec:mt2}

Just as the slepton is a supersymmetric partner to a lepton, the stransverse
mass  $\mttwo$ is a partner to the `transverse mass' $m_T$
(to be defined shortly),
that is useful in searches for supersymmetric particles.

@@

\FloatBarrier
\section{Design}

The most impactful decision in a search is the design of its regions.
Like all decision in life, these designs must be made to balance conflicting
and vaguely-specified desires, and are informed with incomplete information.

@@

>>>>

Summary plots for $\twoljets$-RJR and the former 2 and 3 lepton analysis,
including these signal regions with former excesses,
are displayed in Figure~\ref{fig:2ljets_rjr_summaries}.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
    \caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
    \caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.8\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
    \caption{$\twoljets$ RJR~\cite{atlas2022searches}}
\end{subfigure}
\caption{%
Summary plots for RJR analyses:
(a) and (b)~two- and three- lepton selections respectively reproduced
from~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$ RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\textit{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_rjr_summaries}
\end{figure}

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26\,\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
Please do not read them all in detail.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12\,\eV[G]$ and
\item $\pt^{e_2} > 17\,\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10\,\eV[G]$,
\item $\pt^{\mu_2} > 14\,\eV[G]$,
\item $\pt^{\mu_1} > 18\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$, and
\item $\pt^{\mu_1} > 22\,\eV[G]~\&~\pt^{\mu_2} > 8\,\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17\,\eV[G]~\&~\pt^{\mu_1} > 14\,\eV[G]$,
\item $\pt^{e_1} > 7\,\eV[G]~\&~\pt^{\mu_1} > 24\,\eV[G]$, and
\item $\pt^{e_1} > 26\,\eV[G]~\&~\pt^{\mu_1} > 8\,\eV[G]$.
\end{itemize}
\end{itemize}
The point of listing these is that demonstrate trigger activations are
non-trivial.
This motivates lepton selections which exceed these trigger thresholds,
so as to avoid the need to model their jagged activations.

@@

\subsection{Jets}
Like leptons, hadronic jets are identified with `baseline' and `signal'
requirements with increasingly tight requirements on quality metrics and
kinematics.

@@

\subsubsection{$b$-tagging}
\label{sec:btagging}
Tagging adds labels to objects.
Unlike how electrons and muons are very cleanly separated however, jet tagging
is a more noisy affair.
Taggers are available for various jet properties, such charm flavor ($c$-jet),
bottom flavor ($b$-jet).
Of these, $\twoljets$ uses only $b$-tagging.

@@

\subsection{Stranverse mass $\mttwo$}
\label{sec:mt2}
Just as the slepton is a supersymmetric partner to a lepton, the stransverse
mass  $\mttwo$ is a partner to the `transverse mass' $m_T$
(to be defined shortly),
that is useful in searches for supersymmetric particles.

@@

\FloatBarrier
\section{Design}
The most impactful decision in a search is the design of its regions.
Like all decision in life, these designs must be made to balance conflicting
and vaguely-specified desires, and are informed with incomplete information.

@@

\section{Unblinding}
